---
editor_options: 
  chunk_output_type: console
---

# MCMC Diagnostics {.tabset .tabset-pills}

```{r make-diag-post}
# make a reduced diagnostic posterior: drop out all quantities associated with simulated years
# there is no point in calculating diagnostic summaries for future years
if (length(simulated) > 0) {
  diag_post = suppressMessages(post_remove(post, paste0("[", simulated), ask = FALSE))
} else {
  diag_post = post
}

# discard any node that simply track prior densities, no need to MCMC diagnose them
pr_rm = c(match_params(diag_post, "_pr["), match_params(diag_post, "_pr$"))
diag_post = suppressMessages(post_remove(diag_post, pr_rm, ask = FALSE))
```

```{r discard-rho-upper-tri}
# duplicate correlation parameters do not need to have MCMC diagnostics ran
# those on the diagonal have already been discarded 
# this code discards those in the upper triangle 
rho_params = match_params(diag_post, "rho", type = "base_only")
rho_keep = unlist(lapply(rho_params, function(x) paste0(x, vcov_inds)))
all_rho = match_params(diag_post, "^rho", type = "base_index")
rho_discard = all_rho[!(all_rho %in% rho_keep)]
diag_post = suppressMessages(post_remove(diag_post, rho_discard, ask = FALSE))
```

```{r discard-MIN-HOR}
# specify the nodes where Minam parameters aren't informed by data, and thus need no MCMC diagnostics
discard_params = c(
  "mu_phi_Mb_Ma[LH_type,origin,pop]",
  "^phi_Mb_Ma[year,LH_type,origin,pop]",
  "delta_O0_O1[pop]",
  "mu_psi_O1[origin,pop]",
  "^psi_O1[year,origin,pop]",
  "mu_psi_O2[origin,pop]",
  "^psi_O2[year,origin,pop]"
)

# replace the placeholder index names with the specific elements in question
no_mcmc_diags_Minam = lapply(discard_params, sub_index, pop = j_min) |>
  lapply(sub_index, LH_type = i_spring) |>
  lapply(sub_index, origin = o_hor) |>
  lapply(sub_index, year = ts_yrs) |>
  lapply(unique) |>
  unlist()

# remove these nodes from the posterior samples that will have MCMC diagnostics ran
diag_post = suppressMessages(post_remove(diag_post, params = no_mcmc_diags_Minam, ask = FALSE))
```

```{r mcmc-diag-function}
# a function to get MCMC diagnoses for a group of parameters
# params: a string to match with postpack::match_params()
# L1: a "Level-1" group label; such as component of the model (e.g., LH apportionment)
# L2: a "Level-2" group label; such as type of parameter (e.g., mean, sd, or year-specific value)
# L3: a "Level-3" group label; such as NOR or HOR

summarize_posterior = function(params, L1 = NA, L2 = NA, L3 = NA) {
  # extract the posteriors of interest and format for 'posterior' package
  post_sub = as_draws_df(post_subset(diag_post, params))
  
  # summarize the posteriors
  diags = summarize_draws(post_sub, mean, ~quantile(.x, c(0.025, 0.975)), rhat, ess_mean, ~ess_quantile(.x, probs = c(0.025, 0.975)), mcse_mean, ~mcse_quantile(.x, probs = c(0.025, 0.975)))
  
  # discard any parameters that were the same value every MCMC iteration
  # (will have an NA for rhat)
  diags = diags[!is.na(diags$rhat),]
  
  # append the level names and return
  cbind(
    L1 = L1, L2 = L2, L3 = L3,
    diags
  )
}

summarize_diags = function(diags) {
  
  # add "Monte Carlo CV"
  diags$mccv_mean = diags$mcse_mean/diags$mean
  diags$mccv_q2.5 = diags$mcse_q2.5/diags$`2.5%`
  diags$mccv_q97.5 = diags$mcse_q97.5/diags$`97.5%`
  
  # summarize the summaries
  data.frame(
    L1 = unique(diags$L1),
    L2 = unique(diags$L2),
    L3 = unique(diags$L3),
    match = unique(postpack:::drop_index(diags$variable)),
    n_params = nrow(diags),
    Rhat_1.01 = sum(diags$rhat >= 1.01),
    Rhat_1.05 = sum(diags$rhat >= 1.05),
    Rhat_1.1 = sum(diags$rhat >= 1.1),
    Rhat_1.2 = sum(diags$rhat >= 1.2),
    ess_mean_400 = sum(diags$ess_mean < 400),
    ess_q2.5_400 = sum(diags$ess_q2.5 < 400),
    ess_q97.5_400 = sum(diags$ess_q97.5 < 400),
    mccv_mean_0.05 = sum(diags$mccv_mean > 0.05),
    mccv_q2.5_0.05 = sum(diags$mccv_q2.5 > 0.05),
    mccv_q97.5_0.05 = sum(diags$mccv_q97.5 > 0.05)
  )
}
```

```{r calculate-mcmc-diagnostics}
# containers
diags_out = NULL
summs_out = NULL

# parr recruitment
L1 = "Egg-to-Parr Survival"
L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "White Noise Process SD", "AR(1) Coefficient", "Among-pop Correlation", "Realized")
match = c("alpha", "^beta[", "^lambda$", "sig_lbeta", "sig_Lphi_E_Pb", "kappa_phi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# summer parr mean length
L1 = "Density-Dependent Summer Length"
L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
match = c("omega0", "omega1", "sig_lL_Pb", "rho_lL_Pb", "^L_Pb[")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# LH apportionment
L1 = "Life History Apportionment"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
match = c("mu_pi[1,.]", "sig_Lpi", "rho_Lpi", "^pi[.+,1,.]")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# parr survival from summer to winter tagging
L1 = "Survival From Summer to Winter"
match = c("phi_Pb_Pa[2,.]")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Overwinter survival: Fall Migrants
L1 = "Overwinter Survival"
L2 = c("Intercept", "Slope", "Realized")
base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "^phi_Pa_Mb[year,LH_type,pop]")
match = sub_index(base, year = ".+", LH_type = i_fall, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Fall Migrants"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Overwinter survival: Spring Migrants
L1 = "Overwinter Survival"
L2 = c("Intercept", "Slope", "Realized")
base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "^phi_Pa_Mb[year,LH_type,pop]")
match = sub_index(base, year = ".+", LH_type = i_spring, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Spring Migrants"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Overwinter survival: Process variance
L1 = "Overwinter Survival"
L2 = c("Process SD", "Among Pop. Correlation")
base = c("sig_Lphi_Pa_Mb", "rho_Lphi_Pa_Mb")
tmp_diags = lapply(1:length(base), function(i) summarize_posterior(base[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# growth from summer to spring
# summer parr mean length
L1 = "Summer to Spring 'Growth Factor'"
L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
match = c("theta0", "theta1", "sig_lDelta_L_Pb_Mb", "rho_lDelta_L_Pb_Mb", "^Delta_L_Pb_Mb[")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# trib to LGR Migration survival: NOR 
L1 = "Migration Survival (Trib to LGR)"
L2 = c("Intercept", "Slope", "Realized")
base = c("tau0", "tau1", "^phi_Mb_Ma[.+,LH_type,origin,pop]")
match = sub_index(base, LH_type = i_spring, origin = o_nor, pop = ".", year = ".+")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# trib to LGR Migration survival: HOR 
L1 = "Migration Survival (Trib to LGR)"
L2 = c("Mean", "Realized")
base = list("mu_phi_Mb_Ma[LH_type,origin,pop]", "phi_Mb_Ma[year,LH_type,origin,pop]")
match = sub_index(base, year = ".+", LH_type = i_spring, origin = o_hor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# trib to LGR Migration survival: Process variance
L1 = "Migration Survival (Trib to LGR)"
L2 = c("Process SD", "Among Pop. Correlation")
base = c("sig_Lphi_Mb_Ma", "rho_Lphi_Mb_Ma")
tmp_diags = lapply(1:length(base), function(i) summarize_posterior(base[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# LGR to Ocean Migration survival: NOR
L1 = "Migration Survival (LGR to Ocean)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "^phi_Ma_O0[year,origin]")
match = sub_index(base, year = ".+", origin = o_nor)
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# LGR to Ocean Migration survival: HOR
L1 = "Migration Survival (LGR to Ocean)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "^phi_Ma_O0[year,origin]")
match = sub_index(base, year = ".+", origin = o_hor)
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# LGR to Ocean Migration survival correlation among origins
tmp_diags = summarize_posterior("rho_Lphi_Ma_O0[2,1]", L1 = L1, L2 ="Among-origin Correlation")
tmp_summ =  summarize_diags(tmp_diags)
diags_out = rbind(diags_out, tmp_diags)
summs_out = rbind(summs_out, tmp_summ)

# Probability of Maturing at Age-3: NOR
L1 = "Pr(Mature at Age-3)"
L2 = c("Mean", "Realized")
base = c("mu_psi_O1[origin,pop]", "^psi_O1[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Probability of Maturing at Age-3: HOR
L1 = "Pr(Mature at Age-3)"
L2 = c("Mean", "Realized")
base = c("mu_psi_O1[origin,pop]", "^psi_O1[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Process Variance: Probability of Maturity at Age-3
L1 = "Pr(Mature at Age-3)"
L2 = c("Process SD", "Among-pop Correlation")
base = c("sig_Lpsi_O1", "rho_Lpsi_O1")
tmp_diags = lapply(1:length(base), function(i) summarize_posterior(base[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Probability of Maturing at Age-4: NOR
L1 = "Pr(Mature at Age-4)"
L2 = c("Mean", "Realized")
base = c("mu_psi_O2[origin,pop]", "^psi_O2[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Probability of Maturing at Age-4: HOR
L1 = "Pr(Mature at Age-4)"
L2 = c("Mean", "Realized")
base = c("mu_psi_O2[origin,pop]", "^psi_O2[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Process Variance: Probability of Maturity at Age-4
L1 = "Pr(Mature at Age-4)"
L2 = c("Process SD", "Among-pop Correlation")
base = c("sig_Lpsi_O2", "rho_Lpsi_O2")
tmp_diags = lapply(1:length(base), function(i) summarize_posterior(base[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Year 1 ocean survival
L1 = "Year 1 Ocean Survival"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_phi_O0_O1[origin,pop]", "sig_Lphi_O0_O1[pop]", "rho_Lphi_O0_O1", "phi_O0_O1[year,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Year 2 ocean survival
L1 = "Year 2 Ocean Survival"
L2 = c("Mean")
base = c("mu_phi_O1_O2[origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Year 2 ocean survival
L1 = "Year 3 Ocean Survival"
L2 = c("Mean")
base = c("mu_phi_O2_O3[origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Misc ocean survival
L1 = "Misc Ocean Survival"
L2 = c("Yr1 NOR:HOR Scaler", "Yr 1 AR(1) Coefficient")
base = c("delta_O0_O1[pop]", "kappa_phi_O0_O1[pop]")
match = sub_index(base, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# BON to LGR Migration survival: NOR 
L1 = "Migration Survival (BON to LGR)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "^phi_Rb_Ra[year,origin]")
match = sub_index(base, year = ".+", origin = o_nor)
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# BON to LGR Migration survival: HOR 
L1 = "Migration Survival (BON to LGR)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "^phi_Rb_Ra[year,origin]")
match = sub_index(base, year = ".+", origin = o_hor)
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# LGR to Ocean Migration survival correlation among origins
tmp_diags = summarize_posterior("rho_Lphi_Rb_Ra[2,1]", L1 = L1, L2 ="Among-origin Correlation")
tmp_summ =  summarize_diags(tmp_diags)
diags_out = rbind(diags_out, tmp_diags)
summs_out = rbind(summs_out, tmp_summ)

# Pre-spawn Survival
L1 = "Pre-spawn Survival"
L2 = c("Mean")
match = c("mu_phi_Sb_Sa")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Carcass Correction
L1 = "Carcass Correction Factor"
L2 = c("Among-Pop Mean", "Among-Pop SD", "Pop-Specific")
match = c("mu_z[.]", "sig_z[.]", "^z[.,.]")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Initial adult recruitment
L1 = "Initial Adult Returns"
L2 = c("Age-3", "Age-4", "Age-5")
match = c("Rb\\[[2|3|4],1,1,.\\]", "Rb\\[[2|3|4|5],2,1,.\\]", "Rb\\[[2|3|4|5|6],3,1,.\\]")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Straying
L1 = "Strays"
L2 = c("Realized Total Number", "Age Comp")
match = c(sub_index("^G[.,origin,pop]", origin = o_hor, pop = "."), sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# remove any summaries for nodes that don't have diagnostics
# e.g., if that "parameter" takes on a fixed value in the model
diags_table = summs_out
diags_table = diags_table[diags_table$n_params > 0,]
```

## Summary Table

This table displays summaries of MCMC diagnostics for all unobserved stochastic nodes in the model (excluding those that are not informed by data, such as HOR Minam maturation or HOR smolt survival; these parameters are sampled purely for organizational purposes in the model). Values in cells represent the percentage of parameters of a given type that fail a diagnostic check. E.g., 50% in the "Rhat > 1.05" column means that half of the parameters of that type had $\hat{R}$ values greater than 1.05. Cells with no color indicate no offense and darker reds indicate greater frequency of an offense.

* $\boldsymbol{\hat{R}}$ measures convergence of multiple chains to a common target distribution. Values close to 1 are ideal but values greater than 1.2 should be considered not well-converged (general rules of thumb).
* **ESS** measures the number of effective MCMC samples are available to estimate a given summary statistic of the posterior -- here the posterior mean and quantiles of the 95% equal-tailed CRI. Percentages shown represent the fraction of parameters that have fewer than 400 ESS -- Vehtari et al. [2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full) suggests 400 as a good rule of thumb.
* **MCCV** is Monte Carlo Standard Error of a summary statistic divided by the estimated posterior summary statistic, intended to represent a measure of precision for estimating posterior summary statistics -- here the posterior mean and quantiles of the 95% equal-tailed CRI. Percentages shown represent the fraction of parameters that have greater than 5% MCCV -- which Staton has deemed an acceptable level of imprecision.

The calculations behind this table are implemented using the '[posterior](https://mc-stan.org/posterior/articles/posterior.html)' R package, which contains updated MCMC diagnostics (Vehtari et al. [2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full)).

```{r mcmc-diag-table, warning = FALSE}
# duplicate the diagnostic output
kable_table = diags_table

# order the rows
kable_table$L1 = factor(kable_table$L1, levels = unique(kable_table$L1))
kable_table = diags_table[order(kable_table$L1, kable_table$L2, kable_table$L3),]

# keep only relevant columns for kable
kable_table = kable_table[,-which(colnames(diags_table) %in% c("match", "mean_value", "Rhat_mean", "ess_bulk_mean"))]

# convert counts of offending parameters to percentages
kable_table$Rhat_1.01 = paste0(round(kable_table$Rhat_1.01/kable_table$n_params, 2) * 100, "%")
kable_table$Rhat_1.05 = paste0(round(kable_table$Rhat_1.05/kable_table$n_params, 2) * 100, "%")
kable_table$Rhat_1.1 = paste0(round(kable_table$Rhat_1.1/kable_table$n_params, 2) * 100, "%")
kable_table$Rhat_1.2 = paste0(round(kable_table$Rhat_1.2/kable_table$n_params, 2) * 100, "%")
kable_table$ess_mean_400 = paste0(round(kable_table$ess_mean_400/kable_table$n_params, 2) * 100, "%")
kable_table$ess_q2.5_400 = paste0(round(kable_table$ess_q2.5_400/kable_table$n_params, 2) * 100, "%")
kable_table$ess_q97.5_400 = paste0(round(kable_table$ess_q97.5_400/kable_table$n_params, 2) * 100, "%")
kable_table$mccv_mean_0.05 = paste0(round(kable_table$mccv_mean_0.05/kable_table$n_params, 2) * 100, "%")
kable_table$mccv_q2.5_0.05 = paste0(round(kable_table$mccv_q2.5_0.05/kable_table$n_params, 2) * 100, "%")
kable_table$mccv_q97.5_0.05 = paste0(round(kable_table$mccv_q97.5_0.05/kable_table$n_params, 2) * 100, "%")

# add basic formatting
colnames(kable_table) = c("Model Component", "Parameter Type", "Group", "N", "> 1.01", "> 1.05", "> 1.1", "> 1.2", "Mean", "q2.5", "q97.5", "Mean", "q2.5", "q97.5")
kable_table$Group[is.na(kable_table$Group)] = " "
kable_table$`Parameter Type`[is.na(kable_table$`Parameter Type`)] = " "

assign_color = function(x, colors = c("white","red")) {
  pal = colorRampPalette(colors)
  cols = pal(6)
  bin_names = levels(cut(rbeta(1e6, 1, 1) * 100, breaks = c(0,0.001,20,40,60,80,100), include.lowest = TRUE))
  names(cols) = bin_names
  x[is.na(x)] = 0
  bins = cut(x, breaks = c(0,0.001,20,40,60,80,100), include.lowest = TRUE)
  cols_use = cols[as.character(bins)]
  alpha(unname(cols_use), 0.5)
}

# produce the kable
kable(kable_table, row.names = FALSE, align = c("lllcccccccccc")) %>%
  kable_styling(full_width = TRUE, fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  add_header_above(c(" " = 4, "Rhat" = 4, "ESS < 400" = 3, "MCCV > 5%" = 3)) %>%
  column_spec(2:3, width = "150px") %>%
  column_spec(c(4,8,11), border_right = TRUE) %>%
  column_spec(5, background = assign_color(as.numeric(stringr::str_remove(kable_table[,5], "%")))) %>%
  column_spec(6, background = assign_color(as.numeric(stringr::str_remove(kable_table[,6], "%")))) %>%
  column_spec(7, background = assign_color(as.numeric(stringr::str_remove(kable_table[,7], "%")))) %>%
  column_spec(8, background = assign_color(as.numeric(stringr::str_remove(kable_table[,8], "%")))) %>%
  column_spec(9, background = assign_color(as.numeric(stringr::str_remove(kable_table[,9], "%")))) %>%
  column_spec(10, background = assign_color(as.numeric(stringr::str_remove(kable_table[,10], "%")))) %>%
  column_spec(11, background = assign_color(as.numeric(stringr::str_remove(kable_table[,11], "%")))) %>%
  column_spec(12, background = assign_color(as.numeric(stringr::str_remove(kable_table[,12], "%")))) %>%
  column_spec(13, background = assign_color(as.numeric(stringr::str_remove(kable_table[,13], "%")))) %>%
  column_spec(14, background = assign_color(as.numeric(stringr::str_remove(kable_table[,14], "%")))) %>%
  collapse_rows(columns = 1:2)
```

## Figures {.tabset .tabset-pills}

```{r mcmc-diag-plots-prep}
n_max_draw = 30

# which parameters fall in each Rhat bin
rhat_1_params = subset(diags_out, rhat >= 0.8 & rhat < 1.05)$variable
rhat_2_params = subset(diags_out, rhat >= 1.05 & rhat < 1.1)$variable
rhat_3_params = subset(diags_out, rhat >= 1.1 & rhat < 1.5)$variable

# extract the Rhat values and the names of the parameters with the 
# worst Rhat values by bin
rhat_1 = diags_out$rhat[diags_out$variable %in% rhat_1_params]
rhat_1_params_draw = rhat_1_params[order(rhat_1, decreasing = TRUE)][1:min(n_max_draw, length(rhat_1_params))]
rhat_2 = diags_out$rhat[diags_out$variable %in% rhat_2_params]
rhat_2_params_draw = rhat_2_params[order(rhat_2, decreasing = TRUE)][1:min(n_max_draw, length(rhat_2_params))]
rhat_3 = diags_out$rhat[diags_out$variable %in% rhat_3_params]
rhat_3_params_draw = rhat_3_params[order(rhat_3, decreasing = TRUE)][1:min(n_max_draw, length(rhat_3_params))]

# subset out these parameters: makes postpack::diag_plots() much faster
post_sub_1 = post_subset(post, rhat_1_params_draw)
post_sub_2 = post_subset(post, rhat_2_params_draw)
post_sub_3 = post_subset(post, rhat_3_params_draw)

# function to plot a histogram of rhat values
rhat_hist = function(rhat) {
  par(mgp = c(2,0.35, 0), tcl = -0.15, xaxs = "i", yaxs = "i", mar = c(3,3,1,1))
  breaks = seq(min(rhat), max(rhat), length = 20)
  max_count = max(hist(rhat, breaks = breaks, plot = FALSE)$count)
  hist(rhat, breaks = breaks, col = "grey50", border = "white", ylim = c(0, max_count) * 1.025, xlab = TeX("$\\hat{R}$"), main = "")
  usr = par("usr")
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
  segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE)
}
```

### $1 < \hat{R} < 1.05$ {.tabset .tabset-pills}

#### Distribution

There were **`r length(rhat_1_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes with $\hat{R}$ in this group. Here is their distribution:
  
```{r rhat-hist-1, fig.width = 6, fig.height = 4}
rhat_hist(rhat_1)
```

#### Least Converged

Density and trace plots by chain for the `r min(n_max_draw, length(rhat_1_params))` parameters with the highest $\hat{R}$ values in this group are shown.

```{r mcmc-diag-plots-1, fig.width = 11, fig.height = 8.5}
diag_plots(post_sub_1, ".", show_diags = "never")
```

### $1.05 < \hat{R} < 1.1$ {.tabset .tabset-pills}

#### Distribution

There were **`r length(rhat_2_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes in this group. Here is their distribution:
  
```{r rhat-hist-2, fig.width = 6, fig.height = 4}
rhat_hist(rhat_2)
```

#### Least Converged

Density and trace plots by chain for the `r min(n_max_draw, length(rhat_2_params))` parameters with the highest $\hat{R}$ values in this group are shown.

```{r mcmc-diag-plots-2, fig.width = 11, fig.height = 8.5}
diag_plots(post_sub_2, ".", show_diags = "never")
```

### $\hat{R} > 1.1$ {.tabset .tabset-pills}

#### Distribution

There were **`r length(rhat_3_params)`** of **`r nrow(diags_out)`** unobserved stochastic nodes in this group. Here is their distribution:
  
```{r rhat-hist-3, fig.width = 6, fig.height = 4}
rhat_hist(rhat_3)
```

#### Least Converged

Density and trace plots by chain for the `r min(n_max_draw, length(rhat_3_params))` parameters with the highest $\hat{R}$ values in this group are shown.

```{r mcmc-diag-plots-3, fig.width = 11, fig.height = 8.5}
diag_plots(post_sub_3, ".", show_diags = "never")
```

