---
editor_options: 
  chunk_output_type: console
---

# Parameter Summaries {.tabset .tabset-dropdown}

```{r my-boxplot-function}
my_boxplot = function(params, ylab = NULL, ticklabs = pops, ylim = NULL, boxfill = tran_cols["model"], border = main_cols["model"], las = 3, label_text = NULL, ...) {
  # extract posterior samples and rename them
  post_sub = post_subset(post, params, matrix = TRUE)
  
  if (ncol(post_sub) >= 2) {
    colnames(post_sub) = ticklabs
  }

  # initialize a boxplot object
  bp = boxplot(post_sub, plot = FALSE)
  
  
  # replace the summary stats with my preferred quantiles
  bp$stats = apply(post_sub, 2, function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975)))
  if (is.null(ylim)) ylim = make_lim(bp$stats)
  bxp(bp, ylab = ylab, xlab = "", outline = FALSE, ylim = ylim, las = las, ...,
      staplelty = 0, whisklty = 1, boxfill = boxfill, boxcol = border, medcol = border, whiskcol = border)
  
  axis_labels(ylab = ylab, outer = FALSE, yline = 1)
  panel_label(label_text, "topleft")
} 

ref_line = function(h) {
  abline(h = h, col = par("col.axis"), lty = 2)
}

bp_mar = c(3,2,1,1)
bp_oma = c(0.2,0.2,0,0)
```

## Egg $\to$ Parr Survival {.tabset .tabset-pills}

### Coefficients (BH Parameters)

```{r egg-to-parr-bxp, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("^alpha[.]", "Productivity")
my_boxplot("^beta[.]", "Capacity")
```

### Process SD & Correlation

```{r egg-to-parr-bxp2, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot("^sig_Lphi_E_Pb[.]", "Process SD", ylim = c(0,2))
my_boxplot("^kappa_phi_E_Pb[.]", "AR(1) Coef.", ylim = c(-1,1)); ref_line(h = 0)
my_boxplot(paste0("^rho_Lphi_E_Pb", vcov_inds), "Correlation", ylim = c(-1,1), ticklabs = vcov_labels); ref_line(h = 0)
```

## Parr Mean Length {.tabset .tabset-pills}

### Coefficients

```{r summer-size-bxp1, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("^omega0[.]$", "Intercept")
my_boxplot("^omega1[.]$", "Slope"); ref_line(h = 0)
```

### Process SD & Correlation

```{r summer-size-bxp2, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("^sig_lL_Pb[.]$", "Process SD", ylim = c(0,0.5))
my_boxplot(paste0("^rho_lL_Pb", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); ref_line(h = 0)
```

## Migratory Strategy Apportionment

```{r LH-type-bxp, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot(sub_index("mu_pi[LH_type,pop]", LH_type = i_fall, pop = "."), ylab = "Average Pr(Fall)", ylim = ylim_01)
my_boxplot("sig_Lpi[", "Process SD", ylim = c(0,2))
my_boxplot(paste0("^rho_Lpi", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); ref_line(h = 0)
```

## Overwinter Survival {.tabset .tabset-pills}

### Coefficients

```{r overwinter-survival-bxp1, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_fall, pop = "."), "Intercept", label_text = "Fall Migrants")
my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_spring, pop = "."), "Intercept", label_text = "Spring Migrants")
my_boxplot(sub_index("gamma1[LH_type,pop]", LH_type = i_fall, pop = "."), "Slope", label_text = "Fall & Spring Migrants"); ref_line(h = 0)
```

### Process SD & Correlation

```{r overwinter-survival-bxp2, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("sig_Lphi_Pa_Mb[", "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lphi_Pa_Mb", vcov_inds), "Correlation", ticklabs = vcov_labels); ref_line(h = 0)
```

## Parr $\to$ Smolt "Growth" Factor {.tabset .tabset-pills}

### Coefficients

```{r growth-factor-bxp1, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("^theta0[.]$", "Intercept")
my_boxplot("^theta1[.]$", "Slope"); ref_line(h = 0)
```

### Process SD & Correlation

```{r growth-factor-bxp2, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("^sig_lDelta_L_Pb_Mb[.]$", "Process SD", ylim = c(0,0.5))
my_boxplot(paste0("^rho_lDelta_L_Pb_Mb", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); ref_line(h = 0)
```

## Smolt $\to$ LGR Survival {.tabset .tabset-pills}

### Coefficients

```{r trib-to-lgr-bxp1, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot("tau0", "Intercept", label_text = "NOR")
my_boxplot("tau1", "Slope", label_text = "NOR"); ref_line(h = 0)
my_boxplot(sub_index("mu_phi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_hor, pop = c(1,2,4)), "Average Survival", label_text = "HOR", ticklabs = pops[c(1,2,4)], ylim = ylim_01)
```

### Process SD & Correlation

```{r trib-to-lgr-bxp2, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("sig_Lphi_Mb_Ma[", "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lphi_Mb_Ma", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
```

## LGR $\to$ BON Survival

```{r lgr-to-ocean-bxp, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot("mu_phi_Ma_O0", "Average Survival", ylim = ylim_01, ticklab = origins)
my_boxplot("sig_Lphi_Ma_O0[", "Process SD", ticklab = origins, ylim = c(0,2))
my_boxplot("rho_Lphi_Ma_O0[2,1]", "Correlation (Origins)", ylim = c(-1,1), ticklab = c("")); ref_line(h = 0)
```

## Pr(Mature Age-3) {.tabset .tabset-pills}

### Means

```{r age3-mean-bxp, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_nor, pop = "."), "Pr(Mature Age-3)", label_text = "NOR", ylim = ylim_01)
my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_hor, pop = c(1,2,4)), "Pr(Mature Age-3)", label_text = "HOR", ylim = ylim_01, ticklabs = pops[c(1,2,4)])
```

### Process SD & Correlation

```{r age3-sd-bxp, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("sig_Lpsi_O1[", ylab = "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lpsi_O1", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); ref_line(h = 0)
```

## Pr(Mature Age-4) {.tabset .tabset-pills}

### Means

```{r age4-mean-bxp, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_nor, pop = "."), "Pr(Mature Age-4)", label_text = "NOR", ylim = ylim_01)
my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_hor, pop = c(1,2,4)), "Pr(Mature Age-4)", label_text = "HOR", ylim = ylim_01, ticklabs = pops[c(1,2,4)])
```

### Process SD & Correlation

```{r age4-sd-bxp, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("sig_Lpsi_O2[", ylab = "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lpsi_O2", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); ref_line(h = 0)
```

## Ocean Survival {.tabset .tabset-pills}

### Year 1 {.tabset .tabset-pills}

#### Means

```{r yr1-ocean-bxp, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot(sub_index("mu_phi_O0_O1[origin,.]", origin = o_nor), label_text = "NOR", ylim = ylim_01, ylab = "Average Survival")
my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_hor, pop = c(1,2,4)), label_text = "HOR", ticklabs = pops[c(1,2,4)], ylim = ylim_01, ylab = "Average Survival")
```

#### Process SD & Correlation

```{r yr1-ocean-bxp2, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot("sig_Lphi_O0_O1[", ylab = "Process SD", ylim = c(0,2))
my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "Autocorrelation", ylim = c(-1,1)); ref_line(h = 0)
my_boxplot(paste0("rho_Lphi_O0_O1", vcov_inds), ticklabs = vcov_labels, ylab = "Correlation", ylim = c(-1,1)); ref_line(h = 0)
```

### Year 2 {.tabset .tabset-pills}

```{r yr2-ocean-bxp, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot(sub_index("mu_phi_O1_O2[origin,.]", origin = o_nor), label_text = "NOR", ylim = ylim_01, ylab = "Average Survival")
my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_hor, pop = c(1,2,4)), label_text = "HOR", ticklabs = pops[c(1,2,4)], ylim = ylim_01, ylab = "Average Survival")
```

### Year 3 {.tabset .tabset-pills}

```{r yr3-ocean-bxp, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot(sub_index("mu_phi_O2_O3[origin,.]", origin = o_nor), label_text = "NOR", ylim = ylim_01, ylab = "Average Survival")
my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_hor, pop = c(1,2,4)), label_text = "HOR", ticklabs = pops[c(1,2,4)], ylim = ylim_01, ylab = "Average Survival")
```

### NOR:HOR Log Odds Ratios

```{r ocean-surv-scaler, fig.width = 4, fig.height = 3.5, out.width = "50%"}
mypar(mfrow = c(1,1), mar = bp_mar, oma = bp_oma)
my_boxplot(sub_index("delta_O0_O1[pop]", pop = c(1,2,4)), ylab = "Log Odds Ratio", ticklabs = pops[c(1,2,4)], ylim = c(-1.5,1.5)); ref_line(h = 0)
```

## BON $\to$ LGR Survival

```{r bon-to-lgr-bxp, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot("mu_phi_Rb_Ra", "Average Survival", ylim = ylim_01, ticklab = origins)
my_boxplot("sig_Lphi_Rb_Ra[", "Process SD", ticklab = origins, ylim = c(0,2))
my_boxplot("rho_Lphi_Rb_Ra[2,1]", "Correlation (Origins)", ylim = c(-1,1), ticklab = c("")); ref_line(h = 0)
```

## Pre-spawn Survival

```{r prespawn-surv-bxp, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot("mu_phi_Sb_Sa", "Average Survival", ylim = ylim_01)
my_boxplot("sig_Lphi_Sb_Sa[", "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lphi_Sb_Sa", vcov_inds), "Correlation", ylim = c(-1,1), ticklab = vcov_labels); ref_line(h = 0)
```
